Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
updas
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60924 72bbbca6-d526-0410-a7d9-f06f51895060
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60925 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{multirow}
\usepackage[small,bf]{caption} % CHECK IF THIS IS OK
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}

@@

Tokenisation of the corpus is performed by our morphological analyser. This analyser
performs tokenisation on the basis of a left-to-right longest match algorithm described
in \textcite{garrido02}. Simple tokens such as \emph{толқулар} `riots' are maintained
as a single token, and their lemma and morphological analysis is returned. Multiword
units such as \emph{ауа райы} `weather' and \emph{ата-ананың} `of parents' are combined
into a single token. Abbreviations and numerals which bear case, such as АҚШ-пен `with the USA'
and \emph{90\%-ына} `to the 90\%' are analysed as a single token, as are light-verbs such as
\emph{пайда бол} `to appear' and tense forms written with space like \emph{оқыған жоқ},
the third-person negative past of \emph{оқы} `to learn'.

@@

\begin{table}[htbp]
	\centering
	\begin{tabular}{ll}
		\toprule
		\textbf{Label} & \textbf{Description} \\
		\midrule
				\\
 		\bottomrule
	\end{tabular}
	\caption{Universal dependency label set}
\end{table}

>>>>

\usepackage[normalem]{ulem}
\usepackage{multirow}
\usepackage[small,bf]{caption} % CHECK IF THIS IS OK
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}

@@

Tokenisation of the corpus is performed by our morphological analyser. This analyser
performs tokenisation on the basis of a left-to-right longest match algorithm described
in \textcite{garrido02}. Simple tokens such as \emph{толқулар} `riots' are maintained
as a single token, and their lemma and morphological analysis is returned. Multiword
units such as \emph{ауа райы} `weather' and \emph{ата-анасының} `of their parents' are combined
into a single token. Abbreviations and numerals which bear case, such as АҚШ-пен `with the USA'
and \emph{90\%-ына} `to the 90\%' are analysed as a single token, as are light-verbs such as
\emph{пайда бол} `to appear' and tense forms written with space like \emph{оқыған жоқ},
the third-person negative past of \emph{оқы} `to learn'.

@@

\begin{table}[htbp]
        \centering
\begin{small}
        \begin{tabular}{ll|ll|ll}
                \toprule
                \textbf{Label} & \textbf{Description} & \textbf{Label} & \textbf{Description} & \textbf{Label} & \textbf{Description} \\
                \midrule
\texttt{acl} & clausal modifier of noun & \texttt{\sout{csubjpass}} & clausal passive subject & texttt{\sout{neg}} & negation modifier\\
\texttt{advcl} & adverbial clause modifier & \texttt{dep} & unspecified dependency & \texttt{nmod} & nominal modifier\\
\texttt{advmod} & adverbial modifier & \texttt{det} & determiner & \texttt{\sout{nsubj}} & nominal subject\\
\texttt{amod} & adjectival modifier & \texttt{discourse} & discourse element & \texttt{\sout{nsubjpass}} & passive nominal subject\\
\texttt{appos} & appositional modifier & \texttt{\sout{dislocated}} & dislocated elements & \texttt{nummod} & numeric modifier\\
\texttt{aux} & auxiliary & \texttt{dobj} & direct object & \texttt{parataxis} & parataxis\\
\texttt{\sout{auxpass}} & passive auxiliary & \texttt{\sout{expl}} & expletive & \texttt{punct} & punctuation\\
\texttt{case} & case marking & \texttt{foreign} & foreign words & \texttt{remnant} & remnant in ellipsis\\
\texttt{cc} & coordinating conjunction & \texttt{\sout{goeswith}} & goes with & \texttt{\sout{reparandum}} & overridden disfluency\\
\texttt{ccomp} & clausal complement & \texttt{iobj} & indirect object & \texttt{root} & root\\
\texttt{compound} & compound & \texttt{list} & list & \texttt{vocative} & vocative\\
\texttt{conj} & conjunct & \texttt{mark} & marker & \texttt{xcomp} & open clausal complement\\
\texttt{cop} & copula & \texttt{\sout{mwe}} & multi-word expression & \\
\texttt{\sout{csubj}} & clausal subject & \texttt{name} & name & \\

                \bottomrule
        \end{tabular}
\end{small}
        \caption{Universal dependency label set}
\end{table}
